A New Unitary RG-based Auxiliary Model Approach to Strongly-Correlated Systems

### 2022-03-31 notes/notes.tex
tiled to obtain periodic models

The momentum space Greens function can be expressed as a Fourier transform of the real space Greens functions:
\begin{equation}\begin{aligned}
	G_{H-H} (\vec k, \omega) = \frac{1}{N}\sum_{\vec r, \vec r_j}e^{i \vec{k}\cdot\left(\vec{r_i} - \vec {r_j}\right)}G_{H-H} (|\vec{r_i} - \vec {r_j}|, \omega)
\end{aligned}\end{equation}
where $\vec{r_i}$ is the position vector of a particular lattice site. Because of translation invariance, the real space Greens function depends only on the relative vector between any two sites. As a result, $\vec r=0$ gives the local Greens function, $|\vec r|=a$ gives the nearest-neighbour Greens function and so on ($a$ being the lattice spacing). As we do not have real space Greens function that are more non-local than nearest neighbour, we will attempt to obtain momentum space Greens function from these two contributions:
\begin{equation}\begin{aligned}
	G_{H-H} (\vec k, \omega) \simeq \frac{1}{N}\sum_{\vec{r_i} = \vec {r_j}}\left(G_{H-H} (\omega)\right) _\text{loc} + \frac{1}{N}\sum_{|\vec{r_i} - \vec {r_j}|=a} e^{i \vec{k}\cdot\left(\vec{r_i} - \vec {r_j}\right)}\left(G_{H-H} (\omega)\right)_\text{n-n}
\end{aligned}\end{equation}
The first summation produces a factor of $N$, while the second summation can be factorized into a sum over all sites (which again returns $N$) and a sum over all the primitive vectors connecting any single site with all its nearest neighbours, $\left\{ \vec a_i: i \in \left[1, w\right]\right\}$.
\begin{equation}\begin{aligned}
	\label{k_Gf_siam}
	G_{H-H} (\vec k, \omega) &\simeq G_{H-H} (\omega)_\text{loc} + G_{H-H} (\omega)_\text{n-n}\sum_{i=1}^w e^{i \vec{k}\cdot\vec {a_i}} = G_{H-H} (\omega)_\text{loc} + G_{H-H} (\omega)_\text{n-n} \xi_{\vec k}\\
			     &= \sum_n\left[\left(|d^p_n|^2 + \frac{\xi_{\vec k}}{w}\left(d^p_n\right)^* z^p_n\right) \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn} - \left(|d^h_n|^2 + \frac{\xi_{\vec k}}{w}\left(z^h_n\right)^* d^h_n\right) \left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\right]
\end{aligned}\end{equation}
where we defined \(\xi_{\vec k} \equiv \sum_{i=1}^w e^{i \vec{k}\cdot\vec {a_i}}\). For example, on a d-dimensional hypercubic lattice, we obtain
\begin{equation}\begin{aligned}
	\xi_{\vec k} = \sum_{i=1}^d \left(e^{i k_i {a_i}} + e^{-i k_i {a_i}}\right) = 2\sum_{i=1}^d \cos k_i a_i
\end{aligned}\end{equation}
On a 2D square lattice with lattice spacing $a$, this simplifies to
\begin{eqnarray}
	\label{2dsquaretb}
\xi_{\vec{q}} &=& 2(\cos q_{x}a + \cos q_{y}a)\equiv \frac{-\epsilon_{\vec{q}}}{t^{H}}~,\nonumber\\
\epsilon_{\vec{q}} &=& -2t^{H}(\cos q_{x}a_{x} + \cos q_{y}a_{y})~
\end{eqnarray}
where \(\epsilon_{\vec{q}}\) is the tight-binding dispersion.

@@

With the knowledge of the momentum-space Greens function $G_\text{H-H}(\vec k, \omega)$, we can now use Dyson's equation to calculate the self-energy for propagation of momentum excitations:
\begin{equation}\begin{aligned}
	\Sigma(\vec k,\omega) = G_0(\vec k,\omega)^{-1} - G(\vec k,\omega)^{-1}
\end{aligned}\end{equation}
where the $G_{0}(\vec k, \omega)^{-1}  = \omega -\epsilon_{k} = \omega +t^{H-H}\xi_{k}$ is the inverse $k-$space Greens function for the appropriate non-interacting tight-binding system. Substituting this as well as the full Greens function $G_{H-H}(\vec k, \omega)$ into Dyson's equation gives
\begin{equation}\begin{aligned}
	\Sigma_{H-H}(\vec k,\omega) &= \omega +t^{H-H}\xi_{\vec k} - \left\{\sum_n\left[\left(|d^p_n|^2 + \frac{\xi_{\vec{k}}}{w}\left(d^p_n\right)^* z^p_n\right) \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn} - \left(|d^h_n|^2 + \frac{\xi_{\vec{k}}}{w}\left(z^h_n\right)^* d^h_n\right) \left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\right]\right\}^{-1}\\
&= 	 \omega +t^{H-H}\xi_{\vec k} - \left [G_\text{aux,dd} + \frac{\xi_{\vec k}}{w} G_\text{aux,dz}\right]^{-1}
\end{aligned}\end{equation}
This allows us to calculate the full self-energy $\Sigma (\vec{k},\omega)$ for the Hubbard model on the 2D square lattice.

@@

\section{Analytic consistency check - On the Bethe lattice}
One can apply a test to this method: it involves considering the case of infinite number of nearest-neighbours $w\to\infty$ (the coordination number, and effectively the dimension). Here, as has been argued in the DMFT literature, the correct scaling of the $t^{H}$ hopping parameter is $t^{H}\to t^{H}/\sqrt{w}$ such that the kinetic energy of the associated tight-binding lattice model is finite. This allows for the competition between the kinetic and potential terms of the Hamiltonian to drive a metal-insulator transition in the limit of $w\to\infty$ as well. Further, it has been argued in the DMFT literature that the Greens function matrix of the Hubbard model on the Bethe lattice with $w\to\infty$ becomes purely local (i.e., it has vanishing inter-site matrix elements). We can also see this from eqs.\eqref{green_eq_final_siam}- the nearest-neighbour inverse Greens function vanishes in the limit of $w \to \infty$:
\begin{equation}\begin{aligned}
	\left(\mathcal{G}_{H-H}(\omega)\right)_{ij}^\sigma = \frac{1}{w} \sum_n \left(d^p_n\right)^* z^p_n \left(\mathcal{G}^{-1}_\text{aux}(d, \omega) \right)_{nn} \implies \lim_{w \to \infty}\left(\mathcal{G}_{H-H}(\omega)\right)_{ij}^\sigma \to 0
\end{aligned}\end{equation}
There we used the fact since at half-filling on an $SU(2)$ symmetric model, we expect $\left<\hat n_{i \uparrow} \right> = \frac{1}{2}$, the orthonormal expansion of $c^\dagger_{i \sigma}\ket{\Phi_0} = \sum_n d^p_n \ket{\Phi_n}$ and \(c^\dagger_{i+1,\sigma}\ket{\Phi_0}=z^p_n\ket{\Phi_n}\) are constrained such that $\sum_n |d^p_n|^2 = \sum_n |z^p_n|^2 = \frac{1}{2}$, so that the only term that scales with $w$ is $w$ itself. This result then implies that $G^{H-H}$ matrix has no $k$ dependence.

In this limit, the self-energy also simplifies:
\begin{equation}\begin{aligned}
	\lim_{w \to \infty}\Sigma_H(\vec k,\omega) = = \omega +t^{H-H}\xi_{\vec k} - \left\{\sum_n \left[|d^p_n|^2  \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn}- |d^h_n|^2 \left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\right]\right\}^{-1}
\end{aligned}\end{equation}
We can now see that even in the limit of $w\to\infty$, the competition between ${g}_{0}$ (the on-site repulsion) and the hopping related kinetic energy ($t^{H}\xi_{\vec{k}}$) can lead to a metal-insulator transition.

@@

In summary, the spectral representation of the matrix elements of the inverse Greens operators are given by
\begin{gather}
\label{green_eq_final_siam}
	\left(\mathcal{G}^{-1}_{H-H}(\omega)\right)^p_{ii} = \sum_{n} |d^p_{1,n}|^2 \left(\mathcal{G}^{-1}_\text{aux}(\omega)\right)_{nn}~,\\
	\left(\mathcal{G}^{-1}_{H-H}(-\omega)\right)^h_{ii} = \sum_{n} |d^h_{1,n}|^2 \left(\mathcal{G}^{-1}_\text{aux}(-\omega)\right)_{nn}~,\\
	\left(\mathcal{G}^{-1}_{H-H}\left(\omega\right) \right)^p_{i,i+1} = \frac{2}{w} \sum_n \left[\left(d^p_{1,n}\right)^*d^p_{2,n} + \left(d^p_{1,n}\right)^* z^p_{1,n} + \text{h.c.}\right] \left(\mathcal{G}^{-1}_\text{aux}(\omega) \right)_{nn}~,\\
	\left(\mathcal{G}^{-1}_{H-H}\left(-\omega\right) \right)^h_{i,i+1} = \frac{2}{w} \sum_n \left[\left(d^h_{1,n}\right)^*d^h_{2,n} + \left(d^h_{1,n}\right)^* z^h_{1,n} + \text{h.c.}\right] \left(\mathcal{G}^{-1}_\text{aux}(-\omega) \right)_{nn}~,\\
	\left(\mathcal{G}_\text{H-H}^{-1}\left( \omega \right) \right)^p_{i,i+2} = \frac{2}{w(w-2)}\sum_n \left[\left(d^p_{1,n}\right)^* z^p_{2,n} + \left(z^p_{2,n}\right)^* d^p_{1,n}\right] \left(\mathcal{G}^{-1}_\text{aux}(\omega)\right)_{nn}~,\\
	\left(\mathcal{G}_\text{H-H}^{-1}\left( -\omega \right) \right)^h_{i,i+2} = \frac{2}{w(w-2)}\sum_n \left[\left(d^h_{1,n}\right)^* z^h_{2,n} + \left(z^h_{2,n}\right)^* d^h_{1,n}\right] \left(\mathcal{G}^{-1}_\text{aux}(\omega)\right)_{nn}~.
\end{gather}

@@

The Lehmann-Kallen spectral representation of the single-particle Greens functions can now be written in terms of these matrix elements. Using eq.~\ref{G_mat_el}, we write the on-site ($\left(G_{H-H}(\omega)\right)_\text{loc}$) and nearest neighbour ($\left(G_{H-H}(\omega)\right)_\text{n-n}$) Greens functions as
\begin{equation}\begin{aligned}
	\label{greens_func_siam}
	&\left(G_{H-H}(\omega)\right)_\text{loc} = \left(\mathcal{G}_{H-H}(\omega)\right)_{ii}^p - \left(\mathcal{G}_{H-H}(-\omega)\right)_{ii}^h = \sum_n \left[|d^p_{1,n}|^2 \left(\mathcal{G}_\text{aux}(\omega)\right)_{nn} - |d^h_{1,n}|^2 \left(\mathcal{G}_\text{aux}(-\omega)\right)_{nn}\right] = G_\text{aux}(d_1,d_1;\omega)\\
	&\left(G_{H-H}(\omega)\right)_\text{n-n} = \left(\mathcal{G}_{H-H}(\omega)\right)_{i,i+1}^p - \left(\mathcal{G}_{H-H}(-\omega)\right)_{i+1,i}^h\\
						&\frac{2}{w}\sum_n \left\{\left[\left(d^p_{1,n}\right)^*d^p_{2,n} + \left(d^p_{1,n}\right)^* z^p_{1,n} + \text{h.c.}\right] \left(\mathcal{G}_\text{aux}(\omega) \right)_{nn} - \left[\left(d^h_{1,n}\right)^*d^h_{2,n} + \left(d^h_{1,n}\right)^* z^h_{1,n} + \text{h.c.}\right] \left(\mathcal{G}_\text{aux}(-\omega) \right)_{nn}\right\}\\
						&= \frac{2}{w}\left[G_\text{aux}(d_1,d_2;\omega) + G_\text{aux}(d_1,0_1;\omega) + G_\text{aux}(0_1,d_1;\omega)\right]\\
						&\left(G_\text{H-H}\right)_\text{n-n-n} = \frac{2}{w(w-2)} \left[G_\text{aux}(d_1,0_2;\omega) + G_\text{aux}(0_2,d_1;\omega)\right] 
\end{aligned}\end{equation}

@@

The momentum space Greens function can be expressed as a Fourier transform of the real space Greens functions:
\begin{equation}\begin{aligned}
	G_{H-H} (\vec k, \omega) = \frac{1}{N}\sum_{\vec r, \vec r_j}e^{i \vec{k}\cdot\left(\vec{r_i} - \vec {r_j}\right)}G_{H-H} (|\vec{r_i} - \vec {r_j}|, \omega)
\end{aligned}\end{equation}
where $\vec{r_i}$ is the position vector of a particular lattice site. Because of translation invariance, the real space Greens function depends only on the relative vector between any two sites. As a result, $\vec r=0$ gives the local Greens function, $|\vec r|=a$ gives the nearest-neighbour Greens function and so on ($a$ being the lattice spacing). As we do not have real space Greens function that are more non-local than next-nearest neighbour, we will attempt to obtain momentum space Greens function from these contributions:
\begin{equation}\begin{aligned}
	G_{H-H} (\vec k, \omega) \simeq \frac{1}{N}\sum_{\vec{r_i} = \vec {r_j}}\left(G_{H-H} (\omega)\right) _\text{loc} + \frac{1}{N}\sum_{|\vec{r_i} - \vec {r_j}|=a} e^{i \vec{k}\cdot\left(\vec{r_i} - \vec {r_j}\right)}\left(G_{H-H} (\omega)\right)_\text{n-n}
\end{aligned}\end{equation}
The first summation produces a factor of $N$, while the second summation can be factorized into a sum over all sites (which again returns $N$) and a sum over all the primitive vectors connecting any single site with all its nearest neighbours, $\left\{ \vec a_i: i \in \left[1, w\right]\right\}$.
\begin{equation}\begin{aligned}
	G_{H-H} (\vec k, \omega) &\simeq G_{H-H} (\omega)_\text{loc} + G_{H-H} (\omega)_\text{n-n}\sum_{i=1}^w e^{i \vec{k}\cdot\vec {a_i}} + G_{H-H} (\omega)_\text{n-n-n}\sum_{i=1}^w e^{i \vec{k}\cdot\vec {b_i}}= G_{H-H} (\omega)_\text{loc} + G_{H-H} (\omega)_\text{n-n} \xi_{\vec k} + G_{H-H} (\omega)_\text{n-n-n} \xi^\prime_{\vec k}
\end{aligned}\end{equation}
where we defined \(\left\{b_i\right\} \) as the set of vectors that connect a particular lattice site with its next-nearest-neighbours,\(\xi_{\vec k} \equiv \sum_{i=1}^w e^{i \vec{k}\cdot\vec {a_i}}\) and \(\xi^\prime_{\vec k} \equiv \sum_{j} e^{i \vec{k}\cdot\vec {b_j}}\). Note that \(b_j\) is simply \(a_i + a{i^\prime}\) where \(a_i\) and \(a_{i^\prime}\) are orthogonal.
On a d-dimensional hypercubic lattice, we obtain
\begin{gather}
	\xi_{\vec k} = \sum_{i=1}^d \left(e^{i k_i {a_i}} + e^{-i k_i {a_i}}\right) = 2\sum_{i=1}^d \cos k_i a_i\\
\end{gather}
On a 2D square lattice with lattice spacing $a$, this simplifies to
\begin{eqnarray}
	\label{2dsquaretb}
\xi_{\vec{q}} &=& 2(\cos q_{x}a + \cos q_{y}a)\equiv \frac{-\epsilon_{\vec{q}}}{t^{H}}~,\nonumber\\
\end{eqnarray}
where \(\epsilon_{\vec{q}} = -2t^{H}(\cos q_{x}a_{x} + \cos q_{y}a_{y})\) is the tight-binding dispersion.
\begin{equation}\begin{aligned}
	\label{k_Gf_siam}
	G_{H-H} (\vec k, \omega) = G_\text{aux}(d_1,d_1;\omega) + \frac{2\xi_{\vec k}}{w}\left[G_\text{aux}(d_1,d_2;\omega) + G_\text{aux}(d_1,0_1;\omega) + G_\text{aux}(0_1,d_1;\omega)\right] + \frac{2\xi^\prime_{\vec k}}{w(w-2)} \left[G_\text{aux}(d_1,0_2;\omega) \right.\\
	+ \left.G_\text{aux}(0_2,d_1;\omega)\right]
\end{aligned}\end{equation}

@@

>>>>

The momentum space Greens function can be expressed as a Fourier transform of the real space Greens functions:
\begin{equation}\begin{aligned}
	G_{H-H} (\vec k, \omega) = \frac{1}{N}\sum_{\vec r, \vec r_j}e^{i \vec{k}\cdot\left(\vec{r_i} - \vec {r_j}\right)}G_{H-H} (|\vec{r_i} - \vec {r_j}|, \omega)
\end{aligned}\end{equation}
where $\vec{r_i}$ is the position vector of a particular lattice site. Because of translation invariance, the real space Greens function depends only on the relative vector between any two sites. As a result, $\vec r=0$ gives the local Greens function, $|\vec r|=a$ gives the nearest-neighbour Greens function and so on ($a$ being the lattice spacing). As we do not have real space Greens function that are more non-local than nearest neighbour, we will attempt to obtain momentum space Greens function from these two contributions:
\begin{equation}\begin{aligned}
	G_{H-H} (\vec k, \omega) \simeq \frac{1}{N}\sum_{\vec{r_i} = \vec {r_j}}\left(G_{H-H} (\omega)\right) _\text{loc} + \frac{1}{N}\sum_{|\vec{r_i} - \vec {r_j}|=a} e^{i \vec{k}\cdot\left(\vec{r_i} - \vec {r_j}\right)}\left(G_{H-H} (\omega)\right)_\text{n-n}
\end{aligned}\end{equation}
The first summation produces a factor of $N$, while the second summation can be factorized into a sum over all sites (which again returns $N$) and a sum over all the primitive vectors connecting any single site with all its nearest neighbours, $\left\{ \vec a_i: i \in \left[1, w\right]\right\}$.
\begin{equation}\begin{aligned}
	\label{k_Gf_siam}
	G_{H-H} (\vec k, \omega) &\simeq G_{H-H} (\omega)_\text{loc} + G_{H-H} (\omega)_\text{n-n}\sum_{i=1}^w e^{i \vec{k}\cdot\vec {a_i}} = G_{H-H} (\omega)_\text{loc} + G_{H-H} (\omega)_\text{n-n} \xi_{\vec k}\\
			     &= \sum_n\left[\left(|d^p_n|^2 + \frac{\xi_{\vec k}}{w}\left(d^p_n\right)^* z^p_n\right) \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn} - \left(|d^h_n|^2 + \frac{\xi_{\vec k}}{w}\left(z^h_n\right)^* d^h_n\right) \left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\right]
\end{aligned}\end{equation}
where we defined \(\xi_{\vec k} \equiv \sum_{i=1}^w e^{i \vec{k}\cdot\vec {a_i}}\). For example, on a d-dimensional hypercubic lattice, we obtain
\begin{equation}\begin{aligned}
	\xi_{\vec k} = \sum_{i=1}^d \left(e^{i k_i {a_i}} + e^{-i k_i {a_i}}\right) = 2\sum_{i=1}^d \cos k_i a_i
\end{aligned}\end{equation}
On a 2D square lattice with lattice spacing $a$, this simplifies to
\begin{eqnarray}
	\label{2dsquaretb}
\xi_{\vec{q}} &=& 2(\cos q_{x}a + \cos q_{y}a)\equiv \frac{-\epsilon_{\vec{q}}}{t^{H}}~,\nonumber\\
\end{eqnarray}
where \(\epsilon_{\vec{q}} = -2t^{H}(\cos q_{x}a_{x} + \cos q_{y}a_{y})\) is the tight-binding dispersion.

@@

With the knowledge of the momentum-space Greens function $G_\text{H-H}(\vec k, \omega)$, we can now use Dyson's equation to calculate the self-energy for propagation of momentum excitations:
\begin{equation}\begin{aligned}
	\Sigma(\vec k,\omega) = \left(G^{(0)}(\vec k,\omega)\right)^{-1} - G(\vec k,\omega)^{-1}
\end{aligned}\end{equation}
where $\left(G^{(0)}(\vec k,\omega)\right)^{-1}  = \omega -\epsilon_{k} = \omega +t^{H-H}\xi_{k}$ is the inverse $k-$space Greens function for the appropriate non-interacting tight-binding system. Substituting this as well as the full Greens function $G_{H-H}(\vec k, \omega)$ into Dyson's equation gives
\begin{equation}\begin{aligned}
	\label{self-energy1}
	\Sigma_{H-H}(\vec k,\omega) &= \left(G^{(0)}(\vec k,\omega)\right)^{-1} - \left\{\sum_n\left[\left(|d^p_n|^2 + \frac{\xi_{\vec{k}}}{w}\left(d^p_n\right)^* z^p_n\right) \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn} - \left(|d^h_n|^2 + \frac{\xi_{\vec{k}}}{w}\left(z^h_n\right)^* d^h_n\right) \left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\right]\right\}^{-1}\\
&= \left(G^{(0)}(\vec k,\omega)\right)^{-1} - \left [G_\text{aux,dd} + \frac{\xi_{\vec k}}{w} G_\text{aux,dz}\right]^{-1}
\end{aligned}\end{equation}
This allows us to calculate the full self-energy $\Sigma (\vec{k},\omega)$ for the Hubbard model on the 2D square lattice.

@@

\section{Analytic consistency check - On the Bethe lattice}
One can apply a test to this method: it involves considering the case of infinite number of nearest-neighbours $w\to\infty$ (the coordination number, and effectively the dimension). In such a model, the correct scaling of the $t^{H}$ hopping parameter is $t^{H}\to t^{H}/\sqrt{w}$~\cite{metzner_volhardt_1989,georges_kotliar_1992,pruschke_cox_jarrel_1993}, such that the kinetic energy of the associated tight-binding lattice model remains finite and in competition with the localising physics of \(U\) and the magnetic ordering physics of \(J\). This allows a metal-insulator transition in the limit of $w\to\infty$ as well. In this limit, the dependence of the self-energy on the interacting Greens functin can be shown to arise from only the site-diagonal terms~\cite{Muller-Hartmann1989,georges_kotliar_1992}. This can be demonstrated from the present formalism as well, using eq.\eqref{self-energy1}. Applying the limit of \(w\to \infty\) on that equation gives
	\Sigma_{H-H}(\vec k,\omega) = \lim_{w\to \infty} \left\{\left(G^{(0)}(\vec k,\omega)\right)^{-1} - \left [G_\text{aux,dd} + \frac{\xi_{\vec k}}{w} G_\text{aux,dz}\right]^{-1}\right\} = \lim_{w\to \infty}\left\{G^{(0)}(\vec k,\omega) - G_\text{aux,dd}(\omega)\right\}^{-1} 
where \(G^{(0)}(\vec k,\omega)\) is the non-interacting Greens function and \(G_\text{aux,dd}(\omega)\) is the site-diagonal Greens function of the auxiliary model. It is clear from the final form that only the diagonal term \(G_\text{aux,dd}(\omega)\) of the interacting Greens function affects the self-energy while the off-diagonal part \(G_\text{aux,dz}\) fails to contribute as \(w \to \infty\). Even the non-interacting part Greens function can be shown to be diagonal in the limit of \(w\to\infty\)~\cite{kuramoto_manybody}. From its definition in time domain, we have

@@

In summary, the spectral representation of the matrix elements of the inverse Greens operators are given by
\begin{gather}
\label{green_eq_final_2siam}
	\left(\mathcal{G}^{-1}_{H-H}(\omega)\right)^p_{ii} = \sum_{n} |d^p_{1,n}|^2 \left(\mathcal{G}^{-1}_\text{aux}(\omega)\right)_{nn}~,\\
	\left(\mathcal{G}^{-1}_{H-H}(-\omega)\right)^h_{ii} = \sum_{n} |d^h_{1,n}|^2 \left(\mathcal{G}^{-1}_\text{aux}(-\omega)\right)_{nn}~,\\
	\left(\mathcal{G}^{-1}_{H-H}\left(\omega\right) \right)^p_{i,i+1} = \frac{2}{w} \sum_n \left[\left(d^p_{1,n}\right)^*d^p_{2,n} + \left(d^p_{1,n}\right)^* z^p_{1,n} + \text{h.c.}\right] \left(\mathcal{G}^{-1}_\text{aux}(\omega) \right)_{nn}~,\\
	\left(\mathcal{G}^{-1}_{H-H}\left(-\omega\right) \right)^h_{i,i+1} = \frac{2}{w} \sum_n \left[\left(d^h_{1,n}\right)^*d^h_{2,n} + \left(d^h_{1,n}\right)^* z^h_{1,n} + \text{h.c.}\right] \left(\mathcal{G}^{-1}_\text{aux}(-\omega) \right)_{nn}~,\\
	\left(\mathcal{G}_\text{H-H}^{-1}\left( \omega \right) \right)^p_{i,i+2} = \frac{2}{w(w-2)}\sum_n \left[\left(d^p_{1,n}\right)^* z^p_{2,n} + \left(z^p_{2,n}\right)^* d^p_{1,n}\right] \left(\mathcal{G}^{-1}_\text{aux}(\omega)\right)_{nn}~,\\
	\left(\mathcal{G}_\text{H-H}^{-1}\left( -\omega \right) \right)^h_{i,i+2} = \frac{2}{w(w-2)}\sum_n \left[\left(d^h_{1,n}\right)^* z^h_{2,n} + \left(z^h_{2,n}\right)^* d^h_{1,n}\right] \left(\mathcal{G}^{-1}_\text{aux}(\omega)\right)_{nn}~.
\end{gather}

@@

The Lehmann-Kallen spectral representation of the single-particle Greens functions can now be written in terms of these matrix elements. Using eq.~\ref{G_mat_el}, we write the on-site ($\left(G_{H-H}(\omega)\right)_\text{loc}$) and nearest neighbour ($\left(G_{H-H}(\omega)\right)_\text{n-n}$) Greens functions as
\begin{equation}\begin{aligned}
	&\left(G_{H-H}(\omega)\right)_\text{loc} = \left(\mathcal{G}_{H-H}(\omega)\right)_{ii}^p - \left(\mathcal{G}_{H-H}(-\omega)\right)_{ii}^h = \sum_n \left[|d^p_{1,n}|^2 \left(\mathcal{G}_\text{aux}(\omega)\right)_{nn} - |d^h_{1,n}|^2 \left(\mathcal{G}_\text{aux}(-\omega)\right)_{nn}\right] = G_\text{aux}(d_1,d_1;\omega)\\
	&\left(G_{H-H}(\omega)\right)_\text{n-n} = \left(\mathcal{G}_{H-H}(\omega)\right)_{i,i+1}^p - \left(\mathcal{G}_{H-H}(-\omega)\right)_{i+1,i}^h\\
						&\frac{2}{w}\sum_n \left\{\left[\left(d^p_{1,n}\right)^*d^p_{2,n} + \left(d^p_{1,n}\right)^* z^p_{1,n} + \text{h.c.}\right] \left(\mathcal{G}_\text{aux}(\omega) \right)_{nn} - \left[\left(d^h_{1,n}\right)^*d^h_{2,n} + \left(d^h_{1,n}\right)^* z^h_{1,n} + \text{h.c.}\right] \left(\mathcal{G}_\text{aux}(-\omega) \right)_{nn}\right\}\\
						&= \frac{2}{w}\left[G_\text{aux}(d_1,d_2;\omega) + G_\text{aux}(d_1,0_1;\omega) + G_\text{aux}(0_1,d_1;\omega)\right]\\
						&\left(G_\text{H-H}\right)_\text{n-n-n} = \frac{2}{w(w-2)} \left[G_\text{aux}(d_1,0_2;\omega) + G_\text{aux}(0_2,d_1;\omega)\right] 
\end{aligned}\end{equation}

@@

The momentum space Greens function can be expressed as a Fourier transform of the real space Greens functions:
\begin{equation}\begin{aligned}
	G_{H-H} (\vec k, \omega) = \frac{1}{N}\sum_{\vec r, \vec r_j}e^{i \vec{k}\cdot\left(\vec{r_i} - \vec {r_j}\right)}G_{H-H} (|\vec{r_i} - \vec {r_j}|, \omega)
\end{aligned}\end{equation}
where $\vec{r_i}$ is the position vector of a particular lattice site. Because of translation invariance, the real space Greens function depends only on the relative vector between any two sites. As a result, $\vec r=0$ gives the local Greens function, $|\vec r|=a$ gives the nearest-neighbour Greens function and so on ($a$ being the lattice spacing). As we do not have real space Greens function that are more non-local than next-nearest neighbour, we will attempt to obtain momentum space Greens function from these contributions:
\begin{equation}\begin{aligned}
	G_{H-H} (\vec k, \omega) \simeq \frac{1}{N}\sum_{\vec{r_i} = \vec {r_j}}\left(G_{H-H} (\omega)\right) _\text{loc} + \frac{1}{N}\sum_{|\vec{r_i} - \vec {r_j}|=a} e^{i \vec{k}\cdot\left(\vec{r_i} - \vec {r_j}\right)}\left(G_{H-H} (\omega)\right)_\text{n-n}
\end{aligned}\end{equation}
The first summation produces a factor of $N$, while the second summation can be factorized into a sum over all sites (which again returns $N$) and a sum over all the primitive vectors connecting any single site with all its nearest neighbours, $\left\{ \vec a_i: i \in \left[1, w\right]\right\}$.
\begin{equation}\begin{aligned}
	G_{H-H} (\vec k, \omega) &\simeq G_{H-H} (\omega)_\text{loc} + G_{H-H} (\omega)_\text{n-n}\sum_{i=1}^w e^{i \vec{k}\cdot\vec {a_i}} + G_{H-H} (\omega)_\text{n-n-n}\sum_{i=1}^w e^{i \vec{k}\cdot\vec {b_i}}= G_{H-H} (\omega)_\text{loc} + G_{H-H} (\omega)_\text{n-n} \xi_{\vec k} + G_{H-H} (\omega)_\text{n-n-n} \xi^\prime_{\vec k}
\end{aligned}\end{equation}
where we defined \(\left\{b_i\right\} \) as the set of vectors that connect a particular lattice site with its next-nearest-neighbours,\(\xi_{\vec k} \equiv \sum_{i=1}^w e^{i \vec{k}\cdot\vec {a_i}}\) and \(\xi^\prime_{\vec k} \equiv \sum_{j} e^{i \vec{k}\cdot\vec {b_j}}\). Note that \(b_j\) is simply \(a_i + a{i^\prime}\) where \(a_i\) and \(a_{i^\prime}\) are orthogonal.
On a d-dimensional hypercubic lattice, we obtain
\begin{gather}
	\xi_{\vec k} = \sum_{i=1}^d \left(e^{i k_i {a_i}} + e^{-i k_i {a_i}}\right) = 2\sum_{i=1}^d \cos k_i a_i\\
\end{gather}
On a 2D square lattice with lattice spacing $a$, this simplifies to (same as eq.~\ref{2dsquaretb})
\begin{eqnarray}
\xi_{\vec{q}} &=& 2(\cos q_{x}a + \cos q_{y}a)\equiv \frac{-\epsilon_{\vec{q}}}{t^{H}}~,\nonumber\\
\end{eqnarray}
where \(\epsilon_{\vec{q}} = -2t^{H}(\cos q_{x}a_{x} + \cos q_{y}a_{y})\) is the tight-binding dispersion.
\begin{equation}\begin{aligned}
	G_{H-H} (\vec k, \omega) = G_\text{aux}(d_1,d_1;\omega) + \frac{2\xi_{\vec k}}{w}\left[G_\text{aux}(d_1,d_2;\omega) + G_\text{aux}(d_1,0_1;\omega) + G_\text{aux}(0_1,d_1;\omega)\right] \\
	 + \frac{2\xi^\prime_{\vec k}}{w(w-2)} \left[G_\text{aux}(d_1,0_2;\omega) + G_\text{aux}(0_2,d_1;\omega)\right]
\end{aligned}\end{equation}

@@

\chapter{The Periodic Anderson and Kondo models}
The heavy Fermion systems are described by periodic versions of the single impurity models, where instead a lattice of impurities \(\left\{ d_i \right\} \) hybridises with a conduction bath lattice \(\left\{ i \right\} \). The periodic Anderson model is defined by the Hamiltonian
\begin{equation}\begin{aligned}
	\mathcal{H}_{PAM} = \sum_{k\sigma} \left(\epsilon_k - \mu\right)\tau_{k\sigma} + V\sum_{i,\sigma} \left(c^\dagger_{d_i\sigma}c_{i\sigma} + \text{h.c.} \right)  - \frac{U}{2}\sum_i \left(\hat n_{d_i,\uparrow} - \hat n_{d_i,\uparrow}\right)^2 + \eta \sum_i\tau_{d_i\sigma}
\end{aligned}\end{equation}

As before, we will work with a generalised form of it where we also consider a spin-exchange interaction between the impurity sites and the bath sites:
\begin{equation}\begin{aligned}
	\mathcal{H}_{PAM} = \sum_{k\sigma} \left(\epsilon_k - \mu\right)\tau_{k\sigma} + V\sum_{i,\sigma} \left(c^\dagger_{d_i\sigma}c_{i\sigma} + \text{h.c.} \right) + J \sum_i \vec{S}_{d_i}\cdot\vec{s}_i - \frac{U}{2}\sum_i \left(\hat n_{d_i,\uparrow} - \hat n_{d_i,\uparrow}\right)^2 + \eta \sum_i\tau_{d_i\sigma}
\end{aligned}\end{equation}
One can also introduce an RKKY interaction \(J_\text{RKKY}\) between the nearest neighbour impurity spins:
\begin{equation}\begin{aligned}
	\mathcal{H}_{PAM} = \sum_{k\sigma} \left(\epsilon_k - \mu\right)\tau_{k\sigma} + V\sum_{i,\sigma} \left(c^\dagger_{d_i\sigma}c_{i\sigma} + \text{h.c.} \right) + J \sum_i \vec{S}_{d_i}\cdot\vec{s}_i - \frac{U}{2}\sum_i \left(\hat n_{d_i,\uparrow} - \hat n_{d_i,\uparrow}\right)^2 + \eta \sum_i\tau_{d_i\sigma} \\
	+ J^\prime\sum_{\left<d_i,d_j \right>}\vec{S}_{d_i}\cdot\vec{S}_{d_j}
\end{aligned}\end{equation}

\section{Creating a bulk periodic Anderson model by tiling with generalised single-impurity Anderson models: no RKKY}

The auxiliary model we will be using is a generalised SIAM with attractive interaction on the bath zeroth site and explicit particle-hole asymetry on the impurity:
\begin{equation}\begin{aligned}
	\mathcal{H}_\text{aux} = \sum_{k\sigma}\left(\epsilon_k - \mu\right)\tau_{k\sigma} - \frac{U}{2}\left(\hat n_{d \uparrow} - \hat n_{d \downarrow} \right) ^2 + V \sum_{\sigma} \left(c^\dagger_{0\sigma} c_{d\sigma} + h.c.\right) +J \vec{S_d}\cdot\vec{s}_0 + \eta \sum_\sigma\tau_{d\sigma}
\end{aligned}\end{equation}
where \(\tau = \hat n - 1/2\).
